### 2012-07-18 docs/FAQ/faq.tex
remove references to fParallel
fixed build error
add some bits about debugging and the initial projections

@@

@@

@@

 One implementation of this can be found in {\tt
   fParallel/data\_processing/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.

>>>>

\item {\em Why do the initial projection and ``divu'' iters sometimes
  have a harder time converging than the multigrid solves in the main algorithm?}

  The initial projection and ``divu'' solve sets the density to $1$
  (see \S~\ref{sec:flow:initialization}), so the coefficients in the
  elliptic solve are $O(\beta_0) \sim O(\rho)$.  But in the main
  algorithm, the coefficients are $O(\beta_0/\rho) \sim O(1)$.  Since
  $\rho$ can vary a lot, the variation in the coefficients in the
  initial projection and ``divu'' solve present a harded linear system
  to solve.

@@

\section{Debugging}

@@

\item {\em How can I print out a multifab's contents from within the code?}

  There is a {\tt print} method in {\tt multifab\_module}.  This can
  be simply called as
  \begin{verbatim}
  call print(a)
  \end{verbatim}
  where {\tt a} is a multifab (single-level).

@@

 One implementation of this can be found in {\tt
   AmrPostprocessing/F\_Src/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.
